### 2024-08-27 Chapters/Chapter5.tex
Take out stuff that was outdated after updating data

This is some improvement upon the baseline error, with a decrease in error of around \errorImprovement\%. The power generated by wind mill increases with wind speed cubed\cite{wind_power}. The highest wind gusts in Iceland are around 70 m/s. Knowing the gust factor to 2 percentage points better than before can allow for the anticipated power generated by wind mills to increase significantly.

\section{Discussion}
The error improvement is modest in absolute terms but represents 1.8\% over the baseline.

Training two identical models, one with the transformed reanalysis data and the other with original reanalysis data, results in two near identical errors, as expected. As no new information was input, the data was only manipulated, the model evaluates to the same error. The model that used the transformed reanalysis data was slightly quicker to converge.

Looking only at the error, the performance of the model can be gauged. However it does not help us explain why the model made these predictions. Here feature interpretation can be of great help. Using Shapley values and the python SHAP package, the contribution of each attribute can be given a value, as previously mentioned. Figure \ref{fig:SHAP_final_model} shows the average contribution of each feature.

>>>>

This is some improvement upon the baseline error, with a decrease in error from 23.9\% to 1.8\% depending on the setup used. The power generated by wind mill increases with wind speed cubed\cite{wind_power}. The highest wind gusts in Iceland are around 70 m/s. Knowing the gust factor to 2 percentage points better than before can allow for the anticipated power generated by wind mills to increase significantly.

\section{Discussion}
The error improvement is modest in absolute terms but represents at least 1.8\% over the baseline. Looking only at the error, the performance of the model can be gauged. However it does not help us explain why the model made these predictions. Here feature interpretation can be of great help. Using Shapley values and the python SHAP package, the contribution of each attribute can be given a value, as previously mentioned. Figure \ref{fig:ShapleyWaterfall} shows the contribution of each feature for a given example.

\begin{figure}[h]
    \centering
    \caption[Feature importance for a single observation of a neural network.]{Feature importance of a neural network with model architecture as described in table \ref{table:gridSearchHyperparamters} and data as described in table \ref{table:trainDataExample}. In this specific instance the wind direction ($wd_15$) has the highest negative influence and the temperature has the highest positive influence. Elevation data is excluded when working with Shapley values, as the contribution of each elevation point is very low and there are very many of them. To see their influence on the model output see Table \ref{table:results}.}
    \includegraphics[scale = 0.6]{Figures/waterfall_plot.png}
    \label{fig:ShapleyWaterfall}
\end{figure}

In Figure (\ref{fig:ShapleySummary}) the contribution of each feature, excluding the elevation points, can be seen for the model in general (a significant subset of data is used).

\begin{figure}
    \centering
    \caption[Feature importance of a neural network.]{Feature importance of a neural network with model architecture as described in table \ref{table:gridSearchHyperparamters} and data as described in table \ref{table:trainDataExample}. We can see that generally multiple factors influence the prediction, with the station elevation being highly influential. There is seemingly one outlier for the Richardson number, which usually has very little influence. Elevation data is excluded when working with Shapley values, as the contribution of each elevation point is very low and there are very many of them. To see their influence on the model output see Table \ref{table:results}.}
    \includegraphics[scale = 0.6]{Figures/summary_plot.png}
    \label{fig:ShapleySummary}
\end{figure}
